Supplementary Materials And Methods

### 2019-09-28 Supplementary_mat_met.Rmd
article NAR form

```{r}
data("minsamp")

@@

```{r}
#saveRDS(E9GE_mirnagenenormal, "data/E9GE_mirnagenenormal.rda")

E9GE_mirnagenenormal<-readRDS("data/E9GE_mirnagenenormal.rda")
head(E9GE_mirnagenenormal)
```

@@

```{r}
#saveRDS(E9GE_mirnagenetumor, "data/E9GE_mirnagenetumor.rda")

E9GE_mirnagenetumor<-readRDS("data/E9GE_mirnagenetumor.rda")
head(E9GE_mirnagenetumor)
```

>>>>

```{r}
minsamp<-readRDS("data/minsamp.RDS")

@@

```{r}
E9GE_mirnagenenormal<-readRDS("data/E9GE_mirnagenenormal.RDS")
head(E9GE_mirnagenenormal)
```

@@

```{r}
#saveRDS(E9GE_mirnagenetumor, "data/E9GE_mirnagenetumor.RDS")

E9GE_mirnagenetumor<-readRDS("data/E9GE_mirnagenetumor.RDS")
head(E9GE_mirnagenetumor)
```
